---
title: "Induction Effect"
fig_width: 10
fig_height: 4
keep_md: no
editor_options: 
  chunk_output_type: inline
---

```{r Shape Data}
library(pacman)

p_load(tidyverse, data.table, edgeR, ggplot2, hrbrthemes, viridis, scales, rmarkdown)

doc_theme <- theme_ipsum(
	base_family = "Arial", 
	caption_margin = 12,
	axis_title_size = 12,
	axis_col = "black")

curated_names <- fread(
	"../../curated_names.tsv")

aba.bed <- fread(
	"../../CP046654.1.bed",
	col.names = c(
		"chromosome",
		"left",
		"right",
		"locus_tag",
		"gene_name",
		"strand",
		"coding",
		"completeness"))

aba.counts <- fread(
	"../../all_counts_seal.tsv.gz",
	header = FALSE,
	col.names = c(
		"spacer",
		"count",
		"condition"))

aba.key <- fread(
	"../../aba_key.tsv")

aba.design <- fread(
	"../../ABA1_experimental_design.tsv",
	na.strings = c("NA"))

aba.genome <- aba.key %>% 
	group_by(locus_tag) %>% 
	select(
		locus_tag,
		spacer, 
		type, 
		y_pred, 
		target, 
		offset) %>% 
	inner_join(
		curated_names, 
		by = c("locus_tag" = "AB19606")) %>% 
	rename(AB19606 = locus_tag)

# define the experimental design space to only take into consideration "tubes"
aba.design <- aba.design %>%
	filter(experiment == "tube")

# keep only the counts that are in the experimental design space
aba.counts <- aba.counts %>% semi_join(aba.design)
```

Helper function to convert from dataframe to data.matrix
```{r}
data.matrix.withnames <- function(x) {
    m <- data.matrix(x[,-1], rownames.force = TRUE)
    rownames(m) <- as.data.frame(x)[,1]
    return(m)
}
```

Build up components of bottleneck calculation
```{r message=FALSE}
# https://www.nature.com/articles/nmeth.3253
aba.design <- aba.design %>% 
	mutate(generations = case_when(
		timing == "T0" ~ 0,
		timing == "T1" ~ 9, 
		timing == "T2" ~ 18))

aba.counts.verbose <- aba.counts %>%
	inner_join(aba.design) %>% 
	inner_join(aba.key) %>%
	unite("Condition", drug, dose, timing, sep = "_") %>% 
	unite("Sample",    Condition, rep, sep = "_", remove = FALSE) %>% 
	select(type, spacer, count, Condition, Sample, generations) %>%
	group_by(type) %>%
	nest %>% 
	mutate(
		data = map(
			data, ~pivot_wider(
				.x, 
				id_cols = spacer, 
				names_from = Sample, 
				values_from = count, 
				values_fill = 0)),
		data_matrix = map(
			data, ~data.matrix.withnames(.x)))

aba.group <- aba.design %>%
	as_tibble %>%
	unite("Condition", drug, dose, timing, sep = "_") %>% 
	pull(Condition) %>% 
	factor

aba.permut <- model.matrix( ~ 0 + aba.group)

colnames(aba.permut) <- levels(aba.group)
```

```{r edgeR stuff into the tibbles}
aba.edgeR <- aba.counts.verbose %>% 
	mutate(
		y = map(
			data_matrix, 
			~DGEList(counts = ., group = aba.group, genes = row.names(.))),
		keep = map(
			y,
			~filterByExpr(y = ., design = aba.permut, group = aba.group)),
		y = map2(
			y, 
			keep, 
			~.x[.y, , keep.lib.sizes = FALSE]),
		y = map(
			y,
			~calcNormFactors(.)),
		y = map(
			y,
			~estimateDisp(., aba.permut)),
		fit = map(
			y, 
			~glmQLFit(., aba.permut, robust = TRUE)))
```
Under this paradigm, the fitted values should be equal due to model fitting between replicates.

Thus, we can throw away one replicate and just keep rep. 1 to exhibit the fitted CPM.
```{r Estimate CPM}

aba.cpm <- aba.edgeR %>%
	mutate(
		cpm.fit = map2(
			fit, 
			y, 
			~cpm(y = .x$fitted.values, lib.size = exp(getOffset(.y)))),
		cpm.fit = map(
			cpm.fit, 
			~as_tibble(., rownames = "spacer")),
		cpm.fit = map(
			cpm.fit,
			~pivot_longer(.x, !spacer, names_to = "Sample", values_to = "Fitted CPM")),
		cpm.fit = map(
			cpm.fit,
			~filter(.x, Sample %in% c(
				"None_0_T0_1",
				"None_0_T1_1",
				"None_0_T2_1"))),
		cpm.fit = map(cpm.fit, ~.x %>% mutate(Condition = gsub("_[0-9]$", "", Sample))),
		cpm.fit = map(cpm.fit, ~.x %>% select(Condition, spacer, `Fitted CPM`)),
		cpm.fit = map(cpm.fit, ~.x %>% mutate(Condition = case_when(
			Condition == "None_0_T0" ~ "Uninduced",
			Condition == "None_0_T1" ~ "Induced at t1",
			Condition == "None_0_T2" ~ "Induced at t2"))),
		cpm.fit = map(cpm.fit, ~.x %>% mutate(Condition = factor(
			Condition,
			levels = c(
				"Uninduced",
				"Induced at t1",
				"Induced at t2")))),
		Type = case_when(
			type == "control" ~ "Non-targeting Guides",
			type == "mismatch" ~ "Mismatched Guides",
			type == "perfect" ~ "Perfect Guides"),
		Type = factor(
			Type,
			levels = c(
				"Non-targeting Guides",
				"Mismatched Guides",
				"Perfect Guides")))
```

Do stats to normalize by z-score and change to distribution of controls. https://stats.stackexchange.com/questions/46429/transform-data-to-desired-mean-and-standard-deviation

```{r normalize}
# aba.cpm <- aba.cpm %>%
# 	mutate(
# 		summary = map(
# 		  cpm.fit, 
# 		  ~.x %>% group_by(Condition) %>% 
# 		      summarise(
# 		          mean = mean(`Fitted CPM`) %>% round(3),
# 		          med = median(`Fitted CPM`) %>% round(3),
# 		          min = min(`Fitted CPM`) %>% round(3),
# 		          max = max(`Fitted CPM`) %>% round(3),
# 		          sd = sd(`Fitted CPM`) %>% round(3))),
# 		cpm.fit = map2(
# 			cpm.fit,
# 			summary,
# 			~inner_join(.x, .y) %>% mutate(z = (`Fitted CPM` - mean) / sd )))
# 
# aba.cpm <- aba.cpm %>%
# 	mutate(
# 		cpm.fit = map(
# 			cpm.fit, 
# 			~inner_join(
# 				.x, 
# 				aba.cpm %>% ungroup %>% filter(type == "control") %>% select(summary) %>% unnest(c(summary)), 
# 				by = "Condition")))
# 
# aba.cpm <- aba.cpm %>% mutate(cpm.fit = map(cpm.fit, ~.x %>% mutate(`Normalized Fitted CPM` = z * sd.y + mean.y)))
```

```{r fig.height=3, fig.width=12}
aba.cpm %>% 
	unnest(cpm.fit) %>% 
	select(Type, Condition, `Fitted CPM`) %>% 
	ggplot(aes(x = `Fitted CPM`, fill = `Condition`)) + 
	geom_density() + 	
	scale_fill_viridis(
    discrete = TRUE, 
    alpha = 0.35, 
    direction = -1, 
    option = "cividis") + scale_x_continuous(
        trans = scales::pseudo_log_trans(base = 10),
        breaks = c(0, 10^(1:6)),
        labels = label_number(scale_cut = cut_short_scale())) + 
	facet_wrap(~ Type) + 
	doc_theme

ggsave(
	"Induction_Density.svg", 
	width = 12, 
	height = 3, 
	dpi = 600, 
	units = "in", 
	device = "svg")
```


```{r fig.height=5, fig.width=10}

cpm.max <- aba.cpm %>% 
	ungroup %>% 
	select(cpm.fit) %>% 
	unnest(cols = "cpm.fit") %>% 
	select(`Fitted CPM`) %>% max

aba.cpm.t <- aba.cpm %>%
	mutate(
		plot = map2(
			cpm.fit,
			Type,
			~ggplot(
				.x,
				aes(x = `Fitted CPM`, fill = `Condition`)) +
				geom_density() +
				ggtitle(.y) +
				doc_theme +	
				scale_fill_viridis(
		discrete = TRUE, 
		alpha = 0.3, 
		direction = -1, 
		option = "cividis") +
	scale_x_continuous(
		trans = scales::pseudo_log_trans(base = 10),
		breaks = c(0, 10^(1:6)),
		labels = label_number(scale_cut = cut_short_scale()),
		limits = c(0, cpm.max))))

print(aba.cpm.t$plot)
```

```{r fig.height=5, fig.width=10}

cpm.max <- aba.cpm %>% 
	ungroup %>% 
	select(cpm.fit) %>% 
	unnest(cols = "cpm.fit") %>% 
	select(`Fitted CPM`) %>% max

aba.cpm.t <- aba.cpm %>%
    unnest(cols = c(cpm.fit)) %>%
    group_by(Condition) %>% 
	select(`Type`, `Condition`, spacer, `Fitted CPM`) %>% 
	group_by(Condition) %>% 
	nest %>%
	mutate(
		plot = map2(
			data,
			`Condition`,
			~ggplot(
				.x,
				aes(x = `Fitted CPM`, fill = `Type`)) +
				geom_density() +
				ggtitle(.y) +
				doc_theme +
	scale_fill_viridis(
		discrete = TRUE, 
		alpha = 0.3, 
		direction = -1, 
		option = "magma") +
	scale_x_continuous(
		trans = scales::pseudo_log_trans(base = 10),
		breaks = c(0, 10^(1:6)),
		labels = label_number(scale_cut = cut_short_scale()),
		limits = c(0, cpm.max))))

print(aba.cpm.t$plot)
```

Conditions that we're interested in measuring the differences between

```{r}
conditions.full <- c(
	"None_0_T1 - None_0_T0",
	"None_0_T2 - None_0_T0",
	"Colistin_0.44_T1 - None_0_T0",
	"Colistin_0.44_T2 - None_0_T0",
	"Rifampicin_0.34_T1 - None_0_T0",
	"Rifampicin_0.34_T2 - None_0_T0",
	"Imipenem_0.06_T1 - None_0_T0",
	"Imipenem_0.06_T2 - None_0_T0",
	"Imipenem_0.09_T1 - None_0_T0",
	"Meropenem_0.11_T1 - None_0_T0",
	"Meropenem_0.11_T2 - None_0_T0",
	"Meropenem_0.17_T1 - None_0_T0",
	"Meropenem_0.17_T2 - None_0_T0")

conditions.induction <- c(
	"Colistin_0.44_T1 - None_0_T1",
	"Colistin_0.44_T2 - None_0_T2",
	"Rifampicin_0.34_T1 - None_0_T1",
	"Rifampicin_0.34_T2 - None_0_T2",
	"Imipenem_0.06_T1 - None_0_T1",
	"Imipenem_0.06_T2 - None_0_T2",
	"Imipenem_0.09_T1 - None_0_T1",
	"Imipenem_0.09_T2 - None_0_T2",
	"Meropenem_0.11_T1 - None_0_T1",
	"Meropenem_0.11_T2 - None_0_T2",
	"Meropenem_0.17_T1 - None_0_T1",
	"Meropenem_0.17_T2 - None_0_T2")

conditions.all <- c(conditions.full, conditions.induction)

aba.contrasts <-  makeContrasts(
	contrasts = conditions.all,
	levels = aba.permut)
```

Perform contrasts and find LFC and FDR

```{r}
aba.edgeR <- aba.edgeR %>%
	mutate(
		results = map(
			fit,
			~glmQLFTest(., contrast = aba.contrasts)),
		results = map(
			results,
			~topTags(., n = Inf)),
		results = map(
			results, ~as_tibble(.) %>% pull(table)),
		results = map(
			results, ~rename(., spacer = genes)),
		results = map(
			results, 
			~pivot_longer(
				., 
				!c(spacer, F, PValue, FDR, logCPM), 
				names_to = "contrast", 
				values_to = "logFC")),
		results = map(
			results,
			~inner_join(
				.,
				aba.key %>% select(y_pred, original, locus_tag, offset, spacer))),
		results = map(
			results, 
			~.x %>% mutate(contrast = gsub("\\.\\.\\.", " - ", contrast))),
		results = map(
			results, 
			~.x %>% mutate(contrast = gsub("logFC\\.", "", contrast))),
		summary = map(
			results, 
			~.x %>% group_by(contrast) %>% 
				summarise(
					mean = mean(logFC) %>% round(3),
					med = median(logFC) %>% round(3),
					min = min(logFC) %>% round(3),
					max = max(logFC) %>% round(3),
					sd = sd(logFC) %>% round(3) )),
		summary.paged = map(
			summary, 
			~paged_table(.)))

print(aba.edgeR$type)
print(aba.edgeR$summary.paged)
```

Transpose results: Ungroup from type, then regroup results by contrast group 
```{r}
# aba.edgeR.t <- aba.edgeR %>% 
# 	select(type, results) %>% 
# 	unnest(results) %>% 
# 	group_by(contrast) %>% 
# 	nest %>%
# 	mutate(
# 		plot = map2(
# 			data,
# 			`contrast`,
# 			~ggplot(
# 				.x,
# 				aes(x = `logFC`, fill = `type`)) +
# 				geom_density() +
# 				ggtitle(.y) +
# 				theme_ipsum() +
# 	scale_fill_viridis(
# 		discrete = TRUE, 
# 		alpha = 0.3, 
# 		direction = -1, 
# 		option = "magma")))
# 
# print(aba.edgeR.t$plot)
```

```{r}
# aba.edgeR.prior <- fread("../../Results/melted_results.tsv.gz") %>% 
# 	filter(condition %in% c("None_0_T1 - None_0_T0", "None_0_T2 - None_0_T0")) %>% 
# 	select(type, condition, LFC, LFC.adj) %>% 
# 	group_by(condition) %>% 
# 	nest %>% 
# 	mutate(
# 		plot = map2(
# 			data,
# 			`condition`,
# 			~ggplot(
# 				.x,
# 				aes(x = `LFC.adj`, fill = `type`)) +
# 				geom_density() +
# 				ggtitle(.y) +
# 				theme_ipsum() +
# 				scale_fill_viridis(
# 					discrete = TRUE,
# 					alpha = 0.3,
# 					direction = -1,
# 					option = "magma") +
# 				xlim(
# 					fread("../../Results/melted_results.tsv.gz") %>%
# 						filter(condition %in% c("None_0_T1 - None_0_T0", "None_0_T2 - None_0_T0")) %>%
# 						select(type, condition, LFC, LFC.adj) %>% select(LFC.adj) %>% range)))
# 
# print(aba.edgeR.prior$plot)
```

Show replicates and log2 fold change with respect to T0.

```{r, fig.width=7, fig.height=7}
aba.counts.stats <- aba.counts.verbose %>% 
	select(-data_matrix) %>% 
	unnest(data) %>% 
	pivot_longer(
		!c(type, spacer), 
		names_to = "condition", 
		values_to = "count")

aba.counts.stats <- aba.counts.stats %>% 
	inner_join(
		aba.counts.stats %>%
			filter(condition == "None_0_T0_1") %>%
			ungroup %>%
			rename(base_count = count) %>%
			select(spacer, base_count)) %>% 
	mutate(logFC = log2(count/base_count)) %>%
	rename(sample = condition)

aba.counts.stats <- aba.counts.stats %>% 
	inner_join(
		aba.counts.stats %>% 
			group_by(sample) %>% 
			filter(type == "control") %>% 
			summarise(logFC.med.ctrl = median(logFC))) %>%
	mutate(logFC.adj = logFC - logFC.med.ctrl) %>%
	separate(
		sample, c("drug", "dose", "timing", "rep"), "_") %>%
	mutate(rep = paste("Rep", rep)) %>%
	mutate(dose.with_units = paste0(dose,"ng/μL")) %>%
	unite(
		"Condition", drug, dose.with_units, timing, remove = F) %>% 
	group_by(Condition)

logFC.range <- aba.counts.stats %>% filter(!is.infinite(logFC.adj)) %>% pull(logFC.adj) %>% range

aba.counts.stats.reps <- aba.counts.stats %>% 
	mutate(Type = factor(type)) %>%
	arrange(desc(Type)) %>%
	nest %>% 
	mutate(data = map(
		data,
		~.x %>% pivot_wider(
			id_cols = c(Type, spacer), 
			names_from = rep, 
			values_from = logFC.adj))) %>%
	filter(Condition != "None_0ng/μL_T0") %>% 
	mutate(
		data.finite = map(
			data, ~.x %>% filter(is.finite(`Rep 1`) & is.finite(`Rep 2`))), 
		correlation = map_dbl(data.finite, ~cor(.x$`Rep 1`, .x$`Rep 2`)),
		Title = paste0(
			"LogFC: ", gsub("_", " ", Condition), 
			"(Cor=", round(correlation, 3), ")"))
	

aba.counts.stats.reps <- aba.counts.stats.reps %>%
	mutate(plot = map2(
		data,
		`Title`,
		~ggplot(
			.x,
			aes(x = `Rep 1`, y = `Rep 2`)) +
			geom_abline(intercept = 0, slope = 1, size = 0.5, colour = "red") +
			geom_point(aes(color = Type), shape = 20) +
			ggtitle(.y) +
			doc_theme +
			xlim(logFC.range) +
			ylim(logFC.range) +
			# scale_alpha_manual(values = c(0.5, 0.15, 0.25)) +
			scale_color_viridis(
				discrete = TRUE,
				alpha = c(0.15, 0.25, 0.35),
				direction = -1,
				option = "viridis") +
			theme(
				legend.position = "bottom",
				legend.key = element_rect(fill = "#ECECEC")) +
			guides(colour = guide_legend(override.aes = list(alpha = 1, size = 5))))) 

aba.counts.stats.reps %>% pull(plot) %>% print
```

Violin Plots

```{r}
aba.counts.violin <- aba.counts.stats %>% 
	mutate(rep = paste("Rep", rep)) %>%
	mutate(dose.with_units = paste0(dose,"ng/μL")) %>%
	unite(
		"Condition", drug, dose.with_units, timing, remove = F, sep = " ") %>% 
	filter((Condition %like% "None") & timing != "T0") %>% 
		mutate(
			Condition = gsub("^", "Induction + ", Condition),
			Condition = gsub(" \\+ None 0ng/μL", "", Condition),
			Condition = gsub("(T[1,2])", "at \\1", Condition),
			Condition = factor(Condition, levels = unique(Condition)),
			Condition = factor(Condition, levels = rev(levels(Condition))),
			Type = factor(type),
			Type = factor(Type, levels = rev(levels(Type)))) %>%
	ggplot(aes(x = Condition, y = `logFC.adj`, fill = Type)) + 
	geom_violin(alpha = 0.5, width = 0.65) + 
	doc_theme + 
	scale_fill_viridis(discrete = T, direction = 1, option = "viridis") + 
		coord_flip() +
	  guides(fill = guide_legend(reverse = TRUE)) +
	ggtitle("Distribution of Guide Depletion")

print(aba.counts.violin)
```