---
title: "Suppressor Growth Statistics"
fig_width: 12
fig_height: 4
keep_md: no
editor_options: 
  chunk_output_type: inline
---

# Read raw data

```{r}

library(pacman)

p_load_current_gh("hrbrmstr/hrbrthemes")

p_load(data.table, growthcurver, ggplot2, viridis, tidyverse)


doc_theme <- theme_ipsum(
	base_family = "Arial", 
	caption_margin = 12,
	axis_title_size = 12,
	axis_col = "black")


suppressor_layout <- fread("../../Suppressor/layout.tsv", header = T)
suppressor_OD600  <- fread("../../Suppressor/OD600.tsv")
suppressor_RFP    <- fread("../../Suppressor/RFP.tsv")

suppressor_layout <- melt(
	suppressor_layout, 
	id.vars = "row", 
	value.name = "strain", 
	variable.name = "column")
```

# Perform data wrangling to get data from plate reader format to a useful entry for Growthcurver.

First, OD600 data.

```{r OD600 wrangle}

suppressor_layout[, well := paste0(row, column)]

setnames(suppressor_OD600, t(suppressor_OD600)[, 1])

setnames(
	suppressor_OD600,
	"Cycle Nr.",
	"Well")

suppressor_OD600 <-
	suppressor_OD600[grep("[A-z][0-9]{1,2}", Well)]

suppressor_OD600 <- 
	melt(
		suppressor_OD600, 
		id.vars = "Well", 
		variable.name = "Cycle", 
		value.name = "OD600", 
		na.rm = TRUE)

suppressor_OD600[, Cycle := as.integer(Cycle)]

```

Next, RFP data.

```{r RFP wrangle}

setnames(suppressor_RFP, t(suppressor_RFP)[, 1])

setnames(
	suppressor_RFP,
	"Cycle Nr.",
	"Well")

suppressor_RFP <-
	suppressor_RFP[grep("[A-z][0-9]{1,2}", Well)]

suppressor_RFP <- 
	melt(
		suppressor_RFP, 
		id.vars = "Well", 
		variable.name = "Cycle", 
		value.name = "RFP", 
		na.rm = TRUE)

suppressor_RFP[, Cycle := as.integer(Cycle)]
```

Merge together

```{r Merge}

suppressors <- 
	suppressor_OD600[suppressor_RFP, on = .(Well, Cycle)]

suppressors[, Time := (Cycle - 1) * 60 * 30]

suppressors[, Hour := Time / 60 / 60]

suppressors <- 
	suppressor_layout[, .(Well = well, Strain = strain)][suppressors, on = .(Well)]

```

# Analyze well stats and QC with Growthcurver.

```{r Analyze}

empty_OD600 <- suppressors[, .(min_OD600 = min(OD600)), by = .(Strain)][Strain == "empty", min_OD600]

suppressor_stats <- unique(suppressors[, .(Well, Strain)])

suppressor_stats <- 
	suppressors[
		, SummarizeGrowth(
			Hour, 
			OD600,
			blank = empty_OD600)$vals, 
		by = .(Well, Strain)]

qc_fail <- suppressor_stats[note == "cannot fit data", .(Well, Strain)]

suppressors <- suppressors[!Well %in% qc_fail$Well]

suppressor_stats <- suppressor_stats[!Well %in% qc_fail$Well]

print(paste(qc_fail$Well, qc_fail$Strain, "did not pass quality check."))
```

# Use Growthcurver to extract data fit to model from those wells that passed quality check.

```{r Fit and wrangle data}

fit_suppressors <- suppressors[
	!Well %in% qc_fail$Well,{
		fit <- SummarizeGrowth(Hour, OD600)
		OD600_fit <- fit$model$m$predict()
		Hour <- fit$data$t
		.(Hour, OD600_fit)},
	by = .(Well, Strain)]

fit_suppressors[
	is.na(OD600_fit), 
	OD600_fit := 0]
```

# Identify supprsesor wells ("s") groups where the maximum(RFP) value is greater than the mean of the group (Strain) it belongs to.

These belong to a second group of brightly fluorescing red strains that are actually part of a bimodal distribution.

```{r find bimodal groups}

suppressors <- suppressors[fit_suppressors, on = .(Hour, Well, Strain)]

find_bimodal <- suppressors[, .(maxRFP = max(RFP)), by = .(Well, Strain)]

find_bimodal[Strain %like% "s$", second_type := maxRFP > mean(maxRFP), by = .(Strain)]

suppressors[, second_type := find_bimodal[.SD, on = .(Well)]$second_type]

suppressors[second_type == TRUE, `New Strain` := paste(Strain, "Red")]

suppressors[is.na(`New Strain`), `New Strain` := Strain]

suppressors[, Reps := suppressors[, .N, by = .(Strain, Well)][, .N, by = .(Strain)][.SD, N, on = .(Strain)]]

suppressors[, RFP_norm := RFP - suppressors[Strain == "empty", .(RFP_empty = median(RFP)), by = .(Hour)][.SD, RFP_empty, on = .(Hour)]]
```

# Generate Growth Plots

```{r OD600 by time}
library(pacman)
p_load(data.table, ggplot2, hrbrthemes)

this.plot <- 
    ggplot(
      suppressors[
      	Strain != "empty", 
      	.(OD600, `New Strain` = paste(`New Strain`, Reps, "reps")), 
        by = .(Hour)],
      aes(x = Hour, y = OD600, color = `New Strain`, fill = `New Strain`)) +
    stat_smooth(formula = y ~ s(x, bs = "cs"), method = "gam", level = 0.99) +
		scale_fill_ipsum() +
		scale_color_ipsum() +
		doc_theme +
    ggtitle("Suppressor Growth Stats (OD600), 99% CI")
  
plot(this.plot)

this.plot <- 
    ggplot(
      suppressors[
      	Strain != "empty", 
      	.(OD600_fit, `New Strain` = paste(`New Strain`, Reps, "reps")), 
        by = .(Hour)],
      aes(x = Hour, y = OD600_fit, color = `New Strain`, fill = `New Strain`)) +
    stat_smooth(formula = y ~ s(x, bs = "cs"), method = "gam", level = 0.99) +
		scale_fill_ipsum() +
		scale_color_ipsum() +
		doc_theme +
    ggtitle("Suppressor Growth Stats (OD600 fit), 99% CI")
  
plot(this.plot)

```

# Generate RFP plots.

```{r RFP by time}
this.plot <- 
    ggplot(
      suppressors[
      	Strain != "empty",
        .(RFP_norm, OD600, Strain = paste(Strain, Reps, "reps")), 
        by = .(Hour)],
      aes(x = Hour, y = RFP_norm, color = Strain, fill = Strain)) +
    stat_smooth(formula = y ~ s(x, bs = "cs"), method = "gam", level = 0.50) +
		scale_fill_ipsum() +
		scale_color_ipsum() +
		doc_theme +
    ggtitle("Suppressor Growth Stats (normalized RFP), 50% CI")
  
  plot(this.plot)
  
  this.plot <- 
    ggplot(
      suppressors[
      	Strain != "empty",
        .(RFP_norm, OD600, Strain = paste(Strain, Reps, "reps")), 
        by = .(Hour)],
      aes(x = Hour, y = RFP_norm/OD600, color = Strain, fill = Strain)) +
    stat_smooth(formula = y ~ s(x, bs = "cs"), method = "gam", level = 0.50) +
		scale_fill_ipsum() +
		scale_color_ipsum() +
		doc_theme +
    ggtitle("Suppressor Growth Stats (normalized RFP / OD600), 50% CI")
  
  plot(this.plot)

```

# Barplots to demonstrate RFP knockdown.

```{r RFP at t18}
this_title <- expression(bold(paste("Normalized RFP to" ~ OD[600] ~ "at" ~ hour[18])))

suppressors[Strain != "empty" & Hour == 18] %>%
	ggplot( aes( x = Strain, y = RFP_norm / OD600, fill = Strain)) +
	geom_boxplot( outlier.colour = NA ) +
	scale_fill_viridis( discrete = TRUE, alpha = 0.5) +
	geom_jitter() +
	doc_theme +
	ggtitle(this_title) +
	xlab("Strain")

this_title <- expression(bold(paste("Normalized RFP to" ~ OD[600] ~ "at" ~ hour[18])))

suppressors[Strain != "empty" & Hour == 18] %>%
	mutate(Strain = `New Strain`) %>%
	ggplot( aes( x = `Strain`, y = RFP_norm / OD600, fill = `Strain`)) +
	geom_boxplot( outlier.colour = NA ) +
	scale_fill_viridis( discrete = TRUE, alpha = 0.5) +
	geom_jitter() +
	ggtitle(this_title) +
	xlab("") +
	doc_theme +
	theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

```
